Algebraic Geometry\vspace{-1ex}

### 2019-10-16 Algebraic Geometry/Algebraic-Geometry.tex
update

% Document-Specific Macros

@@

>>>>

% Document-Specific Macros
\newcommand{\SpcFun}{\mathbf{SpcFun}}

@@

\section{October 16}
We're going to finish up with with Yoneda! The milestone for the next week or so: we should have seen and digested some of the 
algebra in the early sections of chapter 2. Max will assume we'll have seen it already starting Friday(ish). We should shoot for having all the problems 
in chapter 2 done by a week from Friday (or so).

\subsection{Old Questions} 
We spoke a bit about lines glued together and the automorphisms of one of the lines that extend to the entire space. 
This necessitates talking about what the automorphisms of $\A1$ are.

We also talked about whether the coordinate axes in $\A3$ are isomorphic as varieties to the projection 
of these axes onto a plane. We discussed that this must induce an isomorphism between the coordinate algebras since they are affine.

\subsection{Back to Yoneda}
Some useful notation for encoding Yoneda: given a functor $F:\calC^{op}\to\Set$, we say that an object $a\in\calC$
\textit{represents} $F$ if $h_a\simeq F$. Then another formulation of Yoneda says that a representing object of a representable functor is unique up to isomorphism of
representing objects.
\begin{center}
	\begin{tikzcd}
		h_a\ar[r,"\sim"]\ar[rr,bend right,"\sim"] & F & h_{a'}\ar[l,"\sim",swap]\\
		& & \\
		& a\to a'&
	\end{tikzcd}
\end{center}
\begin{rmk}
	$h_a$ is called the \textit{functor of points of $a$.}
\end{rmk}
\begin{ex}
Given $f_1\dots,f_n\in k[x_i]$, consider the $k$-algebra $k[x_i]/(f_i)$. Then Yoneda gives us that $A$ is uniquely
determined by the functor 
\[h^A:\Alg_k\to\Set\]
via
\[B\mapsto \Hom(A,B)=\{(b_1,\dots,b_n)\in B^n|f_i(b_1,\dots,b_n)=0\}.\]
\end{ex}
\begin{ex}
	The functor $h_{\P n}:\Alg_k\to\Set$ is 
	\[A\mapsto \{A\twoheadrightarrow L| L\text{ invertible $A$-module}\}/\cong\]
	This is appartently very important.
\end{ex}

\subsection{Representable or not?}
\begin{itemize}
	\item $\Ga$ as a functor from $\SpcFun^{op}\to\Set$ is represented by $\A1$.
	\item $\Gm$ as a functor from $\SpcFun^{op}\to\Set$ is represented by $\A1\setminus\{0\}$.
	\item $\GL_n:\SpcFun^{op}\to\Set$
	\item $|\cdot|:\SpcFun\to\Set$ underlying set 
	\item $\varnothing:\SpcFun^{op}\to\Set$ sending $X\mapsto\varnothing$
	\item $\{\varnothing\}:\SpcFun^{op}\to\Set$ sending $X\mapsto\{\varnothing\}$.
\end{itemize}
